\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{parskip}

\pagestyle{empty}

\begin{document}

\textbf{SYNERGISTIC ACTIVITIES}

\textbf{Name: }Poulsen, Seth

\textbf{ORCID iD: }0000-0001-6284-9972

\textbf{Position Title: }Assistant Professor

\textbf{Primary Organization and Location: }Utah State University, Logan, UT

\textbf{Synergistic Activities:}

\textbf{PrairieLearn Development.} I am on the core development team of PrairieLearn, the open source question and answer platform that will be used in this work. PrairieLearn is used by tens of thousands of students at over a dozen Universities each semester.

\textbf{Statistical Methods in CS Education.} My research work not only pushes the boundaries of knowledge in the field of CS education, but also pushes forward the depth of statistical methods used by those in the field. I have done this by implementing rarely used methods in my work such as Psychometric models, multi-level models, association rule mining, and causal inference.

\textbf{SIGCSE Paper Reviewing.} I am a regular program committee member for the ACM Technical Symposium of the Special Interest Group in Computer Science education, one of the top conferences in computer science education each year.  I have been awarded the `Outstanding Reviewer' award in recognition of my work.

\textbf{Teaching.} I have years of experience in teaching computer science theory content at University of Illinois Urbana-Champaign and Utah State University.

\textbf{Advising Students.} I have successfully advised more than a dozen students on research projects at the undergraduate, Masters, and PhD level.

\end{document}
